Conformal Counterfactual Explanations

### 2023-03-27 paper/paper.tex
first draft for everything excluding experiments and conclusion is done

We propose to include this penalty in the counterfactual search objective (Equation~\ref{eq:general})

>>>>

Penalizing the set size in this way is in principal enough to train efficient conformal classifiers \citep{stutz2022learning}. As we explained above, the set size is also closely linked to predictive uncertainty at the local level. This makes the smooth penalty defined in Equation~\ref{eq:setsize} useful in the context of meeting our objective of generating plausible counterfactuals. In particular, we adapt Equation~\ref{eq:general} to define the baseline objective for Conformal Counterfactual Explanations (CCE):

\begin{equation}\label{eq:cce}
  \begin{aligned}
    \mathbf{s}^\prime &= \arg \min_{\mathbf{s}^\prime \in \mathcal{S}} \left\{  {\text{yloss}(M_{\theta}(f(\mathbf{s}^\prime)),y^*)}+ \lambda \Omega(C_{\theta}(f(\mathbf{s}^\prime);\alpha)) \right\} 
  \end{aligned}
\end{equation}

Since we can still retrieve unperturbed logits from our conformal classifier $M_{\theta}$, we are still free work with any loss function of our choice. For example, we could use standard cross-entropy for $\text{yloss}$.

In order to generate prediction sets $C_{\theta}(f(\mathbf{s}^\prime);\alpha)$ for any Black Box Model we merely need to perform a single calibration pass through a holdout set $\mathcal{D}_{\text{cal}}$. Arguably, data is typically abundant and in most applications practitioners tend to hold out a test data set anyway. Our proposed approach for CCE therefore removes the restriction on the family of predictive models, at the small cost of reserving a subset of the available data for calibration.
